method

### 2021-12-02 06_Paper/ER-ED/method.Rmd
added libraries

library(targets) # to keep track of all relevant files
library(readxl) # import excel files
library(here) # to set directories without defined paths
library(papaja) # APA conform output

>>>>

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(ggplot2)    # for nice plots
